\newpage
\section{Summary}
In publication 1, the encoding efficiency of passband-bSSFP was improved using a 3D stack-of-spirals acquisition combined with parallel imaging at a challenging ultra-high field strength, thereby improving the practicality of bSSFP-BOLD to a level comparable with the popular \gls{GE}-\gls{EPI}. To improve image quality, we incorporated a slice-selective binomial pulse for fat suppression and a reconstruction model that accounts for system imperfections such as trajectory deviations and spatial $B_0$ inhomogeneity. The computational cost and memory requirements for reconstructing undersampled 3D data in non-Cartesian grid was minimized through the efficient \gls{NUFFT} algorithm, segmented modeling of $B_0$ effects for deblurring, and sampling-density-based pre-conditioning to accelerate convergence of the iterative solver. We further explored the acquisition parameters (e.g., TR and TE) space afforded by the non-Cartesian bSSFP sequence and proposed optimal protocols to maximize functional sensitivity. Functional activation maps obtained from both high-resolution thin-slab (0.6 mm and 0.8 mm isotropic) and whole-brain (1.2 mm isotropic) experiments exhibited localized activation without geometric distortion. 

In publication 2, we demonstrated \gls{bSSFP} acquisition techniques and novel processing methods to enhance the sensitivity of \gls{DMI}. Two encoding variants, i.e., \gls{CSI} and multi-echo of \gls{bSSFP} acquisition were tested in phantom measurements and subject measurements with oral [6,6'-$^2H_2$]-glucose intake. We demonstrated that phase cycling provides off-resonance insensitivity and additional spectral encoding, offering an extra degree of freedom beyond the conventional Dixon encoding.  All protocols were optimized for maximal SNR based on the measured \textit{in vivo} relaxation times of deuterium metabolites at 9.4~T. A notable observation was that the reference method, based on the vendor's 3D \gls{CSI} implementation, utilized optimized protocols for efficient averaging and SNR-performant \gls{FISP}/\gls{SSFP}-\gls{FID} acquisition with no RF spoiling. Consequently, the achieved SNR enhancement of up to 25\% was lower than improvements reported in preclinical studies~\cite{petersImprovingDeuteriumMetabolic2021,montraziHighsensitivityDeuteriumMetabolic2023}, which employed protocols prioritizing spectral resolution with lower \gls{SNR} performance and RF-spoiled FLASH acquisition as their reference method. All designed protocols, including the reference protocol, achieved a substantially improved spatial resolution of 2.7–4.3 mL (equivalent to an acquisition-weighted 0.4–0.6 mL nominal resolution, as reported in the literature) while maintaining a temporal resolution of 10 minutes. The desirable \gls{PSF} of acquisition-weighting used in the \gls{CSI} variant showed a better \gls{SNR} performance than the uniform k-space weighting of the multi-echo \gls{bSSFP} variant. The flexibility of the proposed IDEAL-modes algorithm greatly simplifies the processing of phase-cycled spectroscopic bSSFP data and produces reliable metabolite maps without the explicit knowledge of the spatial off-resonance map, flip angle map, and relaxation times of the deuterium metabolites. The spectral resolution was sufficient to reliably separate the glucose uptake and downstream metabolites in the brain.   

In summary, two established advantages of bSSFP, i.e., its spin-echo-like behavior to improve the specificity of fMRI and its high signal efficiency for chemical species with large $T_2/T_1$ ratios to enhance human DMI, were utilized to develop \gls{UHF} methodologies to improve  brain function investigations at 9.4 T.

