
\section{Journal Articles}

\begin{enumerate}

\item Submillimeter balanced SSFP BOLD–functional MRI  accelerated with 3D stack-of-spirals at 9.4 T.\newline
\normalsize \textbf{Praveen Iyyappan Valsala}, Marten Veldmann, Dario Bosch,  Klaus Scheffler, Philipp Ehses.\newline
Published in: \textit{Magnetic Resonance in Medicine} \newline
DOI: \href{https://doi.org/10.1002/mrm.30064}{10.1002/mrm.30064}

\item High-resolution deuterium metabolic imaging of the human brain at 9.4\,T using bSSFP spectral-spatial acquisitions.\newline
\normalsize \textbf{Praveen Iyyappan Valsala}, Rolf Pohmann, Rahel Heule, Georgiy A. Solomakha, Nikolai I. Avdievich, Jörn Engelmann, Laura Kuebler, André F. Martins, Klaus Scheffler.\newline
Published in: \textit{Magnetic Resonance in Medicine I hope}\newline
DOI: \href{https://doi.org/10.1002/mrm.70114}{10.1002/mrm.70114}

\item Easy scalable, low‐cost open‐source magnetic field detection system for evaluating low‐field MRI magnets using a motion‐tracked robot. \newline
\normalsize Pavel Povolni, Robin Bendfeld, Sergej Maltsev, Judith Samlow, Felix Glang, \textbf{Praveen Iyyappan Valsala}, Dominique Goerner, Dario Bosch, Sebastian Mueller, Florian Birk, Kai Buckenmaier, Klaus Scheffler.\newline
Published in: \textit{Magnetic Resonance Materials in Physics, Biology and Medicine}\newline
DOI: \href{https://doi.org/10.1007/s10334-025-01239-1}{10.1007/s10334-025-01239-1}
\end{enumerate}

\section{Conference Abstracts}

\begin{enumerate}

\item  Iyyappan Valsala P, Ehses P, Veldmann M, Scheffler K. Accelerated 3D stack-of-spiral bSSFP for functional imaging at 9.4T: Pilot study. In: 1102, Proc. ISMRM 2022. 
\item  Iyyappan Valsala P, Ehses P, Veldmann M, Scheffler K. Rapid and high-resolution bSSFP fMRI using 3D stack of spirals at 9.4 T. In: Proc. Intl. Soc. Mag. Reson. Med. 2023.
\item  Glang, F.; Iyyappan Valsala, P.; Nikulin, A.; Avdievich, N.; Steffen, T.; Scheffler, K.: Investigations on non-Cartesian parallel imaging with time-varying receive sensitivities. In: Proc. Intl. Soc. Mag. Reson. Med. 2023.
\item  Iyyappan Valsala P, Pohmann R, Heule R, et al. Combining multi-echo and phase cycling in bSSFP acquisition to improve whole-brain deuterium metabolic imaging at 9.4 T. In: Proc. Intl. Soc. Mag. Reson. Med. 32 (2024). Singapore; 2024. 
\item  Kuebler, L.; Iyyappan Valsala, P.; Avdievitch, N.; Engelmann, J.; Scheffler, K.; Martins, A.; Pohmann, R.: Advancing Deuterium Metabolic Imaging Technology for Precise In Vivo Monitoring of Glucose Metabolism: From Bench to Bedside. 19th European Molecular Imaging Meeting (EMIM), 2024
\item  Heule, R.; Valsala, P.; Engelmann, J.; Charyasz, E.; Scheffler, K.: Inverted BOLD signal changes in the transient phase of passband balanced SSFP. In: Proc. Intl. Soc. Mag. Reson. Med. 32 (2024). Singapore; 2024.
\item  Bause, J.; Valsala, P.; Bosch, D.; Ehses, P.; Avdievich, N.; Scheffler, K.: Design and application of a 16-channel field-probe insert for a 16Tx/32 Rx coil at 9.4 Tesla. In: Proc. Intl. Soc. Mag. Reson. Med. 32 (2024). Singapore; 2024.
\item  Iyyappan Valsala, P.; Heule, R.; Ehses, P.; Veldmann, M.; Scheffler, K.: Investigation of bSSFP frequency response changes during a functional experiment at 9.4 T. In Magnetic Resonance Materials in Physics, Biology and Medicine, 37 (Supplement 1), O67, S. S111 - S113. 40th Annual Scientific Meeting of the European Society for Magnetic Resonance in Medicine and Biology (ESMRMB), 2024. 
	
\end{enumerate}

\newpage
\chapter{Statement of contributions}
\huge Submillimeter balanced SSFP BOLD–functional MRI  accelerated with 3D stack-of-spirals at 9.4 T

\normalsize
\begin{itemize}
\item Praveen Iyyappan Valsala: Study design, MR sequence programming, Protocol optimization, MRI measurements, Data analysis, Image reconstruction and Manuscript writing.
\item Marten Veldmann: MR sequence programming
\item Dario Bosch:  MR sequence programming
\item Klaus Scheffler: Study design, Funding acquisition , Supervision 
\item Philipp Ehses: Study design, MR sequence programming, Supervision
\end{itemize}
all : Manuscript-review and editing

\huge High-resolution deuterium metabolic imaging of the human brain at 9.4 T using bSSFP spectral-spatial acquisitions

\normalsize
\begin{itemize}
\item Praveen Iyyappan Valsala: Study conception and design, MR sequence programming, Protocol optimization, Data analysis, MRI measurements, Manuscript writing.
\item Rolf Pohmann : Study conception and design, MR sequence programming, Protocol optimization, MR measurements, Ethics protocol.
\item Rahel Heule : Study conception and design, MR sequence programming.
\item Georgiy A. Solomakha : MR coils and safety
\item Nikolai I. Avdievich : MR coils and safety 
\item Jörn Engelmann : Phantom construction
\item Laura Kuebler: Subject recruitment , Ethics protocol
\item André F. Martins :  Subject recruitment, Ethics protocol and Supervision
\item Klaus Scheffler : Study design, Funding acquisition and Supervision
\end{itemize}
all : Manuscript-review and editing

\newpage

\huge Easy scalable, low‐cost open‐source magnetic field detection system for evaluating low‐field MRI magnets using a motion‐tracked robot

\normalsize
\begin{itemize}
\item Pavel Povolni: study conception and design, acquisition of data, analysis and interpretation of data, drafting of manuscript. 
\item Robin Bendfeld: study conception and design, analysis and  interpretation of data, drafting of manuscript. 
\item Sergej Maltsev: acquisition of data, analysis and interpretation of data. 
\item Judith Samlow: acquisition of data, analysis and interpretation of data. 
\item Felix Glang: analysis and interpretation of data. 
\item \textbf{Praveen Iyyappan Valsala}: analysis and interpretation of data. 
\item Dominique Goerner: analysis and interpretation of data. 
\item Dario Bosch: acquisition of data, analysis and interpretation of data. 
\item Sebastian Mueller: acquisition of data, analysis and interpretation of data. 
\item Florian Birk: analysis and interpretation of data. 
\item Kai Buckenmaier: study conception and design, drafting of manuscript. 
\item Klaus Scheffler: study conception and design.
\end{itemize}
all : Manuscript-review and editing

