% ===================================================================
% ENGLISH ABSTRACT
% ===================================================================

\chapter{Abstract}

\Gls{MRI} has become an indispensable diagnostic tool for clinicians and a powerful investigative technique for researchers. Even after more than five decades after its inception, the field of MRI continues to undergo substantial and consistent advances in technology, methodology, and applications. \Gls{MRI} can sense a wide range of nuclei in the human body, from abundant hydrogen (\textsuperscript{1}H) to less abundant so-called ‘X-nuclei’ such as deuterium (\textsuperscript{2}H), carbon (\textsuperscript{13}C), sodium (\textsuperscript{23}Na), and phosphorus (\textsuperscript{31}P). This capability enables the measurement of morphology, micro-structures, and a wide range of physiological parameters, including blood oxygenation, metabolism, perfusion, tissue stiffness, pH, and temperature, with varying degrees of success. Currently, significant research is focused on \gls{UHF} ($\geq 7\,T$) MR techniques to improve the much-needed sensitivity and explore distinct contrast mechanisms at such high fields. This work is a compilation of two projects, which primarily focus on the methodological development of a rapid image acquisition scheme called \gls{bSSFP} for investigating brain function at \gls{UHF}. \Gls{bSSFP} is known for its high \gls{SNR} efficiency and its characteristic $T_2/T_1$ contrast highlighting fluids, which has traditionally made it popular for cardiac imaging at lower field strengths. 

The first project aims at improving the acquisition efficiency of bSSFP-based \gls{fMRI} using fast and efficient non-Cartesian trajectories in combination with parallel imaging. The aim is to develop a distortion-free \gls{fMRI} method with improved spatial localization of neuronal activity for \gls{UHF} applications, as an alternative to the popular \gls{GE}-\gls{EPI}. The micro-vascular sensitivity of \gls{bSSFP}, similar to that of spin echo sequences, is expected to provide better localization of the \gls{BOLD} signal to sites of neuronal activation. Moreover, the inherently lower radio frequency power deposition of \gls{bSSFP} compared to other spin-echo sequences is advantageous at high fields. However, images acquired at such spatio-temporal resolutions are highly susceptible to minor imperfections in the imaging hardware. Therefore, system imperfections, including eddy current effects and spatial $B_0$ inhomogeneity, were incorporated into the reconstruction model to improve image quality. The utility and flexibility of the developed acquisition and reconstruction method were demonstrated using sub-millimeter protocols with limited coverage and 1.2\,mm-isotropic whole-brain visual functional experiments. Furthermore, the isolated effects of \gls{TR} and \gls{TE} on \gls{bSSFP}-\gls{BOLD} contrast were investigated by analyzing relative signal change, significance of activation, and thermal and temporal signal stability.

In the second project, the combination of \gls{UHF} and \gls{bSSFP} acquisition was explored to improve the sensitivity of \gls{DMI}. \Gls{DMI} is an emerging molecular \gls{MRSI} technique that probes metabolism using a non-radioactive, deuterium-labeled exogenous tracer, typically $[6,6^2-^2H_2]$-Glucose. Unlike the gold standard radioactive \textsuperscript{18}F-FDG used in \gls{PET}, which is not metabolized, deuterated glucose can be metabolized, providing additional information about downstream metabolic pathways. This is a key advantage in the brain, where overall glucose uptake is typically very high. Despite these advantages, the low gyromagnetic ratio of deuterium and low metabolite concentrations often render the technique impractical. On the positive note, the short $T_1$ resulting from pronounced quadrupolar relaxation of deuterium nuclei and the sparse deuterium spectrum support faster signal averaging. These advantages, when combined with the \gls{SNR} enhancements from \gls{UHF} and \gls{bSSFP}, the latter resulting from the large $T_2/T_1$ ratio of deuterium metabolites, give \gls{DMI} a competitive edge over other MR molecular imaging techniques, such as \gls{CEST}, proton (\textsuperscript{1}H) \gls{MRSI}, and \textsuperscript{13}C MRI. Challenges associated with large $B_0$ inhomogeneity in the human head were addressed using phase cycling, albeit at the cost of SNR, to obtain off-resonance insensitive whole-brain metabolite maps. The novel processing method introduced in this work for estimating metabolite amplitudes from phase-cycled \gls{bSSFP} data provides greater flexibility by operating without requiring explicit knowledge of the spatial off-resonance map, flip angle map, or relaxation times of the deuterium metabolites.

Overall, this work highlights both the potential and the challenges of novel \gls{UHF} steady-state techniques for advancing functional and metabolic investigations of the human brain.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End:
