
% ===================================================================
% ACKNOWLEDGMENTS
% ===================================================================

\chapter{Acknowledgments}
This work would not be possible without the technical and emotional support of the following people and numerous unmentioned kind souls who helped along the way.

Firstly, I would like to thank Klaus for accepting me as a PhD student and for the continuous support throughout these long years. The trust and freedom I was given created the ideal environment to develop as an independent researcher.

I thank Fritz Schick, Andreas Bartels, Andre F. Martins, and Prof. XXX? for their roles on my advisory board and examination committee. I am also grateful to Oliver Bieri? for serving as an additional reviewer of my thesis.

A special and heartfelt thanks goes to the "Kinderzimmer" members: Professor, Meister (of Linux) Bosch, 2x Nico (Helmi and NOT-Helmi), HRH Aaron, Dr. (B\"ose)$^{-1}$ M\"uller , the old Paul and the new Tim, for creating such a fun-filled workplace and for ensuring an endless supply of cookies. As the information hub of MRZ, the Kinderzimmer made sure you never missed a thing while also offering countless opportunities to learn from others. The daily educational series (the famous Glang lectures) ranging from dinosaurs to music, politics, philosophy, and, occasionally, even MRI get you covered for the life outside of academia. Furthermore, I would like to express gratitude to the following people.


\begin{itemize}[left=0pt]
	%\setlength{\itemindent}{0pt}
	%\setlength{\leftmargin}{0pt}
	\item[] Rahel: Thank you for all the bSSFP consultations and for your meticulous "swiss-quality" editing service for my manuscripts.
	\item[] Kengo: Thank you for the late-night work buddy and for being a fun "Sensei" outside of work. 
	\item[] Flo and Dana: Thank you for adopting me at work and for being my workout buddies.
	\item[] Pavel: I really enjoyed working with the "allerbeschde Handwerker" from the planet Melmac.
	\item[] Georgiy: Thnak you for being the reliable lunch buddy and a non-judgmental coil consultant.
	\item[] Ju and Giesela : Thank you for the support during the initial days.
	\item[] Rolf: Thank you for introducing me to x-nuclei and spectroscopy.
	\item[] Philipp, Chris, and Marten for their external technical support on sequences and reconstruction.
\end{itemize}

Many many thanks to all other MPI members for all help through these many years: Jonas, KaiB, and KaiH, Rui, Elisa, "Mein freund" Cihan, Lucas, Julius, Egor, Ali, Rebekka, Edyta, Jiazheng, Emiliy, Loreen, Nikolai, Anagha, J\"orn, Yi , Gabi, Qi, Alex and Mihai. Also, a big thanks to Tina for taking care of the endless administrative tasks.

A big thank you goes to all my poor subjects and co-pilots, who endured the long scan times in the name of science.

Finally, I would like to thank my family for their constant love and support, and for giving meaning to all that I do.

\begin{flushright}
  \textit{Praveen Iyyappan Valsala}\\
  T\"ubingen, Spetember, 2025
\end{flushright}

