\newpage
\section{Research Objectives}

The desired outcome of this thesis is to improve upon \gls{UHF} methodology with steady-state acquisitions for two neuroscience applications: \gls{fMRI} (described in \cref{sec:fmri}) and \gls{DMI} (described in \cref{sec:DMI}). The objective of the first part of this thesis is to accelerate the acquisition of the proposed passband-\gls{bSSFP} \gls{fMRI}\cite{bowenHighFieldBalancedSSFP2005,schefflerHighresolutionMappingNeuronal2016} to levels competitive with the established \gls{GE}-\gls{EPI}, which is currently over three times faster. The primary motivation for performing \gls{bSSFP}-\gls{fMRI} is its microvascular specificity, similar to other spin-echo sequences, which aims to improve the accuracy of \gls{BOLD} signal localization by mitigating the macrovascular bias and geometric distortion that can compromise spatial resolution gains achieved at \gls{UHF}\cite{baez-yanezImpactVesselSize2017,schefflerBOLDSensitivityRapid2019}. Moreover, the short readout times afforded by \gls{bSSFP} reduce $T_2^*$-related blurring and off-resonance-related distortions, particularly relevant at \gls{UHF}. A 3D stack-of-trajectories was chosen as the preferred encoding scheme to minimize inflow effects while maintaining a balance between acquisition speed and flexibility. Previous \gls{bSSFP} functional studies have proposed highly-segmented 3D EPI\cite{ehsesMultilineBalancedSSFP2018,millerFMRIUsingBalanced2012} and even spiral readouts\cite{leeFullbrainCoverageHighresolution2008} to accelerate bSSFP acquisition.  However, current \gls{GE}-\gls{EPI} is a mature and optimized technique employing numerous acceleration strategies, including parallel imaging, partial Fourier, and sometimes RF encoding via simultaneous multi-slice. Therefore, to achieve state-of-the-art acquisition speeds, parallel imaging must be incorporated.  Furthermore, challenges at \gls{UHF}, such as highly off-resonant fat signal, must be suppressed for low-bandwidth spiral readout, and residual spatial off-resonance induced blurring must be adequately corrected using deblurring algorithms. Given the acquisition of several hundred volumes for functional studies, the computational cost and memory footprint of the reconstruction model must be minimized. Finally, the isolated effect of \gls{TE}, \gls{TR} and flip angle has to be determined to propose hih-resolution \gls{fMRI} protocols to maximize the functional sensitivity.


As a second topic, we investigated the sensitivity improvements of \gls{DMI} with \gls{bSSFP} to enable high-resolution molecular imaging at \gls{UHF}. The inherently low MR sensitivity of deuterium nuclei and their low \textit{in vivo} concentrations have historically resulted in Glucose-\gls{DMI} investigations in the human brain being performed at low nominal spatio-temporal resolutions, ranging from 3 mL in 10 min at 9.4 T to 14 mL in 39 min at 3 T~\cite{ruhmDeuteriumMetabolicImaging2021, defeyterDeuteriumMetabolicImaging2018, seresroigDeuteriumMetabolicImaging2023, niessWholebrainDeuteriumMetabolic2024, adamsonDeuteriumMetabolicImaging2024}. This clinical translation study was motivated by encouraging preclinical results demonstrating 2-3 times SNR improvement with \gls{bSSFP} compared to spoiled \gls{GRE} sequences, attributable to the favorable $T_2/T_1$ ratio of deuterium metabolites. To mitigate significant spatial $B_0$ inhomogeneity at 9.4 T, phase-cycling was employed to reduce off-resonance sensitivity. However, the addition of phase cycling introduces complex signal modulation that must be accounted for in the signal model during spectral separation. Therefore, accurate signal models are essential for optimizing \gls{SNR} of the measurement protocol and estimating metabolite concentrations. As off-resonance effects due to chemical shifts and spatial $B_0$ inhomogeneity are indistinguishable, estimation of accurate spatial off-resonance maps is warranted for reliable metabolite quantification. The sparse deuterium spectrum, with four observable resonances (water, glucose, glutamate/glutamine, and lactate/lipid) separated by approximately 1 ppm, allows use of two spectroscopic image encoding schemes: conventional \gls{CSI} and multi-echo. The SNR performance and spectral resolution of these two \gls{bSSFP} variants with phase cycling were compared with the reference vendor’s standard \gls{CSI} implementation in phantom and in vivo studies with oral [6,6'-$^2H_2$]-glucose intake.